---
title: "Plurality Voting R code"
author: "Jacky Lyu"
date: "14/08/2022"
output: html_document
---

Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("/Users/jackil/Desktop/Unimelb/2022/Semester 2/SCI30001 Plurality voting Project")
```

## R Markdown

## R codes for research project "Comparison of election auditing methods for plurality contests".
## Completed by Jacky Lyu, in supervision of Dr Damjan Vukcevic

Create CSV datasets
```{r}
# n=number of ballots, pT = true proportion of votes to the first candidate
tc_create_csv <- function(n, pT, name1, name2){
  Yn = c()
  for (i in 1:n){
    Xn = rbinom(1,1,prob=pT)
    if (Xn == 1){
      Yn = append(Yn, name1)
    } else {
      Yn = append(Yn, name2)
    }
  }
  df = data.frame(ballot = Yn)
  return(df)
}

tc_df = tc_create_csv(100, 0.5, "Damjan", "Alex")
write.csv(tc_df, "/Users/jackil/Desktop/Unimelb/2022/Semester 2/SCI30001 Plurality voting Project/Two candidate.csv")

```


SPRT & BRAVO for two candidates
```{r}

# Find winner between two candidates
tcfind_winner = function(data){
  votes = table(data$ballot)
  if (votes[1] > votes[2]){
    return (names(votes)[1])
  } else {
    return (names(votes)[2])
  }
}

# BRAVO Audit for two-candidate voting.
BRAVO <- function(data, alpha, pR){
  # find true parameters in the data
  wT = tcfind_winner(data)
  n = length(data$ballot)
  max_size = 100
  
  # perform iterative sampling algorithm
  Test_Stat = 1
  for (i in 1:max_size){
    Xi = sample(data$ballot, 1)
    if (Xi == wT){
      Test_Stat = Test_Stat*pR/0.5
    } else {
      Test_Stat = Test_Stat*(1-pR)/0.5
    }
    
    if (Test_Stat > 1/alpha){
      return (c(i, 1))
    }
  }  
  return(c(max_size, 0))
}

#compare results
compare_results <- function(data, reported, true){
    if (reported == true) {
      return (1)
    } else {
      return (0)
    }
}
```


Implement Simulation for two candidate ballots
```{r}
tc_simulation <- function(pT, pR, trials, alpha){
  correct_simulations = 0
  sample_sizes = c()
  for (trail in 1:trials) {
    data = tc_create_csv(10000, pT, "Damjan", "Alex")
    BRAVO_result = BRAVO(data, alpha, pR)
    sample_size = BRAVO_result[1]
    outcome = BRAVO_result[2]
    
    if ((pT>0.5) & (outcome == 1)){
      correct_simulations = correct_simulations + 1
    } else if ((pT<=0.5) & (outcome ==0)) {
      correct_simulations = correct_simulations + 1
    }
    
    sample_sizes = append(sample_sizes, sample_size)
  }
  power = correct_simulations/trials
  mean_sample = mean(sample_sizes)
  
  return (c(power, mean_sample))
}


```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
