---
title: "Two candidate BRAVO R File"
author: "Jacky Lyu"
date: "14/08/2022"
output: html_document
---

Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("/Users/jackil/Desktop/Unimelb/2022/Semester 2/SCI30001 Plurality voting Project")
```

## R Markdown

## R codes for research project "Comparison of election auditing methods for plurality contests".
## Completed by Jacky Lyu, in supervision of Dr Damjan Vukcevic

Create CSV datasets
```{r}
# n=number of ballots, pT = true proportion of votes to the first candidate, 
# create a vector of samples
tc_create_csv <- function(n, pT, name1, name2){
  Yn = rbinom(n, 1, pT)
  Yn = ifelse(Yn==1, name1, name2)
  return (Yn)
}  

tc_df = tc_create_csv(10000, 0.5, "Damjan", "Alex")
write.csv(tc_df, "/Users/jackil/Desktop/Unimelb/2022/Semester 2/SCI30001 Plurality voting Project/Two candidate.csv")

```


SPRT & BRAVO for two candidates
```{r}
# Find true winner between two candidates
tcfind_winner = function(data){
  votes = table(data)
  if (votes[1] > votes[2]){
    return (names(votes)[1])
  } else {
    return (names(votes)[2])
  }
}

# Find true loser between two candidates
tcfind_loser = function(data){
  votes = table(data)
  if (votes[1] < votes[2]){
    return (names(votes)[1])
  } else {
    return (names(votes)[2])
  }
}

# Find the true proportion of votes for a reported winner
find_proportion = function(data, reported_name){
  count = sum(data == reported_name)
  size = length(data)
  return (count/size)
}

# BRAVO Audit for two-candidate voting.
# returns a list containing the number of  samples tested and a boolean variable. 
# True indicates certified/reject Ho, False indicates discertifed
tc_BRAVO <- function(data, alpha, wR, pR, max_size = 1000){
  # find true proportion of reported winner in the data
  pT = find_proportion(data, wR)
  
  # perform iterative sampling algorithm
  X = sample(data, max_size)
  TS = ifelse(X == wR, pR/0.5, (1-pR)/0.5)
  TS = cumprod(TS)
  for (i in 1:length(TS)){
    if (TS[i] >= 1/alpha){
      sample_size = i
      return (list(sample_size, TRUE))
    }
  }
  return (list(max_size, FALSE))
}
```


Simulation function for two candidate ballots, for a given pT, pR
```{r}
# perform one simulation on the BRAVO. Returns mean sample size, power, and significiance level.
tc_simulation <- function(pT, pR, ntrials=1000, trial_size=10000, alpha=0.05){
  
  correct_certifications = 0
  incorrect_certifications = 0
  
  data = tc_create_csv(trial_size, pT, "Damjan", "Alex")
  
  #first, set the reported probability with the reported winner as true winner (correct report) 
  wT = tcfind_winner(data)
  
  correct_winner_trials = replicate(ntrials, tc_BRAVO(data, alpha, wT, pR))
  cw_sample_sizes = correct_winner_trials[1,]
  cw_outcomes = correct_winner_trials[2,]
  correct_certifications = sum(cw_outcomes == TRUE)
  
  power = correct_certifications/ntrials
  
  #then, test the reported probability with an actually false reported winner (false report)
  lT = tcfind_loser(data)
  
  false_winner_trials = replicate(ntrials, tc_BRAVO(data, alpha, lT, pR))
  fw_sample_sizes = false_winner_trials[1,]
  fw_outcomes = false_winner_trials[2,]
  incorrect_certifications = sum(fw_outcomes == TRUE)
  
  sig_level = incorrect_certifications/ntrials
  
  #lastly, calculate the mean sample size tested
  mean_sample_size = mean(unlist(list(cw_sample_sizes, fw_sample_sizes)))
  
  return (list(power, sig_level, mean_sample_size))
}
```

Run Simulation over a range of inputs
```{r}
# True proportion and reported proportion values wish to be tested
pT = rep(c(0.52,0.55,0.60), 3)
pR = c(rep(0.7, 3), rep(0.55, 3), rep(0.51, 3))
tc_BRAVO_input = data.frame(pT, pR)
                          
power = c()
sig_level = c()
mean_sample_size = c()

# record power, sig level, mean sample size for each pair of pT, pR tested
for (i in 1:length(tc_BRAVO_input$pT)){
 outcome = tc_simulation(tc_BRAVO_input$pT[i],tc_BRAVO_input$pR[i])
 power[i] = outcome[1]
 sig_level[i] = outcome[2]
 mean_sample_size[i] = outcome[3]
}

# output results as a dataframe
tc_BRAVO_result = data.frame(pT, pR, unlist(power), unlist(sig_level), unlist(mean_sample_size))
colnames(tc_BRAVO_result) = c("pT", "pR", "Power", "Significance Level", "Mean Sample Size")
write.csv(tc_BRAVO_result, "/Users/jackil/Desktop/Unimelb/2022/Semester 2/SCI30001 Plurality voting Project/Two candidate result.csv")


```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
