---
title: "Two candidate BRAVO R File"
author: "Jacky Lyu"
date: "14/08/2022"
output: html_document
---

Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

## R codes for research project "Comparison of election auditing methods for plurality contests".
## Completed by Jacky Lyu, in supervision of Dr Damjan Vukcevic

Create datasets
```{r}

tc_df = tc_create_data(10000, 0.5, "Damjan", "Alex")

```


SPRT & BRAVO for two candidates
```{r}
# Find the true proportion of votes for a reported winner
find_proportion = function(data, reported_name){
  count = sum(data == reported_name)
  size = length(data)
  return (count/size)
}

# BRAVO Audit for two-candidate voting.
# returns a list containing the number of  samples tested and a boolean variable. 
# True indicates certified/reject Ho, False indicates discertifed
tc_BRAVO <- function(data, alpha, wR, pR, max_size = 8000){
  # find true proportion of reported winner in the data
  pT = find_proportion(data, wR)
  
  # perform iterative sampling algorithm
  X = sample(data, max_size, replace = FALSE)
  TS = ifelse(X == wR, pR/0.5, (1-pR)/0.5)
  TS = cumprod(TS)
  for (i in 1:length(TS)){
    if (TS[i] >= 1/alpha){
      sample_size = i
      return (list(sample_size, TRUE))
    }
  }
  return (list(max_size, FALSE))
}
```


Simulation function for two candidate ballots, for a given pT, pR
```{r}
# perform one simulation on the BRAVO. Returns mean sample size, power, and significiance level.
tc_BRAVO_simulation <- function(pT, pR, ntrials=1000, trial_size=10000, alpha=0.05){
  
  certifications = 0
  
  data = tc_create_data(trial_size, pT, "Damjan", "Alex")
  
  trials = replicate(ntrials, tc_BRAVO(data, alpha, "Damjan", pR))
  sample_sizes = trials[1,]
  sample_outcomes = trials[2,]
  certifications = sum(sample_outcomes == TRUE)
  
  certification_rate = certifications/ntrials
  
  #lastly, calculate the mean sample size tested
  mean_sample_size = mean(unlist(sample_sizes))
  
  return (list(certification_rate, mean_sample_size))
}
```

Run Simulation over a range of inputs
```{r}
# True proportion and reported proportion values wish to be tested
number_of_pT = 6
number_of_pR = 3

pT = rep(c(0.4, 0.45, 0.5, 0.52,0.55,0.60), number_of_pR)
pR = c(rep(0.7, number_of_pT), 
       rep(0.55, number_of_pT), 
       rep(0.51, number_of_pT))

tc_BRAVO_input = data.frame(pT, pR)
                          
certification_rate = c()
mean_sample_size = c()

# record power, sig level, mean sample size for each pair of pT, pR tested
for (i in 1:length(tc_BRAVO_input$pT)){
 outcome = tc_BRAVO_simulation(tc_BRAVO_input$pT[i],tc_BRAVO_input$pR[i])
 certification_rate[i] = outcome[1]
 mean_sample_size[i] = outcome[2]
}

# output results as a dataframe
tc_BRAVO_result = data.frame(pT, pR, unlist(certification_rate), unlist(mean_sample_size))
colnames(tc_BRAVO_result) = c("pT", "pR", "Certification Rate", "Mean Sample Size")

```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
